\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-03-06 reviews/response.Rmd

ToDo.

> p8, l44: "Between each month requires some small amount of white space, denoted by b." - strange sentence; rephrase

Done.

> p11, l44: "star plots": briefly explain what these are and cite a basic reference for these.

> Fig.7: Where is "noon" and "midnight" here - on top/bottom or on the 0/180 degree position on the right/left side? And what is the direction? I suppose clockwise, but this needs to be mentioned somewhere.

The start plots have been removed from the paper, since it doesn't add more information to other existing plots.

> p13, l28: "swapped in the Equation 1." -> "swapped in Equation (1)."

> p13, l39: "Figure 13 shows the same plot as Figure 12 labelled": You can't jump forward to a figure before all intermediate figures have been introduced. The previous fig was Fig.8. Figs 9-11 have not been mentioned yet. Either rearrange your figures so that 12-13 become 9-10, or use Chinese characters for one of the previously introduced figs (1-8).

Sure. "Figure 13 shows the same plot as Figure 12 labelled" is deleted.

> p13, possible subsection 2.2.6: You seem to have a "sunday = FALSE" default. If TRUE, does this make Sunday the start of the week (as used in the US & Canada)? If so, mention this as an option. No need for a figure.

Done. More to fill in the section

> p13, possible subsection 2.2.7: How can you enter specific holidays? These are different from country to country, e.g., based on national holidays such as Thanksgiving, Labor Day, independence days, religious holidays, etc.

> Fig.8: "impossible to compare the size of peaks between days." - Correct; since this is based on ggplot, could you use colors from a sequential color scheme that maps the counts, e.g., from faint yellow (0) to dark red (for the overall max)? This might be another
useful argument for a future extension of your function.

> p15, l5: "distinct temporal trend" -> "distinct temporal pattern"

> p15, l12: "idea of faceting": explain what "faceting" means in general (and cite 1 or 2 main references)

> p15, l16: "In particular, it can be immediately learned that when Birrarung Marr was busy and packed, for example Australian Open in the last two weeks of January." -> "In particular, it can be immediately learned that Birrarung Marr was busy and packed, for example during the Australian Open, a major international tennis tournament, in the last two weeks of January."

> p15, l45: "the day before Christmas, go shopping on the Boxing day, and stay out for the fireworks on New Year's Eve.": Some of these names may not be known to non-Christian / non-British readers. List the date in parentheses, e.g., December 24, December 26, etc.

### 2019-03-06 main.Rmd
done with revision pg3 from reviewer 3

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. Figure \ref{fig:fs-polar} shows star plots embedded in the monthly calendar layout, which is equivalent to Figure \ref{fig:fs-2016} placed in polar coordinates. The bimodal work day shape is also visible as boomerangs.

```{r fs-polar, fig.height = 7, fig.cap = "Figure \\ref{fig:fs-2016} in circular layout, which is referred to as star plots. The daily periodicity on work days are clearly visible."}
```

@@

Most countries have adopted this western calendar layout, while the languages used for week day and month would be different across countries. We also offer languages other than English for text labelling. Figure \ref{fig:chn-embedded} shows the same plot as Figure \ref{fig:boxplot} labelled using simplified Chinese characters.

@@

Plots can be layered. The comparison of sensors can be done by overlaying plot the values for each (Figure \ref{fig:overlay}). Differences between the pedestrian patterns at these sensors can be seen. Flagstaff Station exhibits strong commuters patterns, with fewer pedestrian counts during the weekends and public holidays. This suggests that Flagstaff Station has limited functionality on non-work days. From Figure \ref{fig:overlay} it can be seen that Birrarung Marr has a distinct temporal pattern from the other two all year round. The nighttime events, such as White Night, have barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to the State Library and Birrarung Marr.

@@

To avoid the overlapping problem, the calendar layout can be embedded into a series of subplots for the different sensors. Figure \ref{fig:facet} presents the idea of faceting calendar plots. This allows comparing the overall structure between sensors, while emphasizing individual sensor variation. In particular, it can be immediately learned that when Birrarung Marr was busy and packed, for example during the Australian Open, a major international tennis tournament, in the last two weeks of January. This is concealed in the conventional graphics.

>>>>

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. The resulting plot is star glyphs embedded in the monthly calendar layout. Star glyphs are time series lines transformed in polar coordinates.

```{r fs-polar, fig.height = 7, fig.cap = "Figure \\ref{fig:fs-2016} in circular layout, which is referred to as star plots. The daily periodicity on work days are clearly visible.", eval = FALSE}
```

@@

Most countries have adopted this western calendar layout, while the languages used for week day and month would be different across countries. We also offer language specifications other than English for text labelling.

### Start of the week

@@

Plots can be layered. The comparison of sensors can be done by overlaying the values for each (Figure \ref{fig:overlay}). Differences between the pedestrian patterns at these sensors can be seen. Flagstaff Station exhibits strong commuters patterns, with fewer pedestrian counts during the weekends and public holidays. This suggests that Flagstaff Station has limited functionality on non-work days. From Figure \ref{fig:overlay} it can be seen that Birrarung Marr has a distinct temporal pattern from the other two all year round. The nighttime events, such as White Night, have barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to the State Library and Birrarung Marr.

@@

To avoid the overlapping problem, the calendar layout can be embedded into a series of subplots for the different sensors. Figure \ref{fig:facet} presents the idea of faceting calendar plots. This allows comparing the overall structure between sensors, while emphasizing individual sensor variation. In particular, it can be immediately learned that Birrarung Marr was busy and packed, for example during the Australian Open, a major international tennis tournament, in the last two weeks of January. This is concealed in the conventional graphics.

### 2019-03-06 main.tex
done with revision pg3 from reviewer 3

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on
the data. The computation is similar to the one described in
\citet{Wickham2012glyph}. Figure \ref{fig:fs-polar} shows star plots
embedded in the monthly calendar layout, which is equivalent to Figure
\ref{fig:fs-2016} placed in polar coordinates. The bimodal work day
shape is also visible as boomerangs.

{\centering \includegraphics[width=\textwidth]{figure/fs-polar-1}

\caption{Figure \ref{fig:fs-2016} in circular layout, which is referred to as star plots. The daily periodicity on work days are clearly visible.}\label{fig:fs-polar}
\end{figure}

@@

Most countries have adopted this western calendar layout, while the
languages used for week day and month would be different across
countries. We also offer languages other than English for text
labelling. Figure \ref{fig:chn-embedded} shows the same plot as Figure
\ref{fig:boxplot} labelled using simplified Chinese characters.

>>>>

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on
the data. The computation is similar to the one described in
\citet{Wickham2012glyph}. The resulting plot is star glyphs embedded in
the monthly calendar layout. Star glyphs are time series lines
transformed in polar coordinates.

@@

Most countries have adopted this western calendar layout, while the
languages used for week day and month would be different across
countries. We also offer language specifications other than English for
text labelling.

\hypertarget{start-of-the-week}{%
\subsubsection{Start of the week}\label{start-of-the-week}}
